Interoception Scale (Study 2) - Data Cleaning

### 2025-12-29 study2/analysis/1_cleaning.qmd
added internal consistency for MAIA subscales

>>>>

## Internal Consistency

- MAIA [x]
- MINT []
- BPQ []
- IAS []
- TAS-20 []
- B-ERS []
- CERQ-Short []
- CEFSA-14 []
- PI-18 []
- SILS (only one item)
- PHQ-4 []

```{r}
df[grepl("^MAIA_.*_R$", names(df))] <- 6 - df[grepl("^MAIA_.*_R$", names(df))]  # Reverse
maia_ar <- df[, grepl("^MAIA_AttentionRegulation_", names(df))]
maia_bl <-  df[, grepl("^MAIA_BodyListening_", names(df))]
maia_ea <-  df[, grepl("^MAIA_EmotionalAwareness_", names(df))]
maia_nd <-  df[, grepl("^MAIA_NotDistracting_", names(df))]
maia_n <-  df[, grepl("^MAIA_Noticing_", names(df))]
maia_nw <-  df[, grepl("^MAIA_NotWorrying_", names(df))]
maia_sr <-  df[, grepl("^MAIA_SelfRegulation_", names(df))]
maia_t <-  df[, grepl("^MAIA_Trusting_", names(df))]

psych::omega(maia_ar, nfactors = 1)
psych::omega(maia_bl, nfactors = 1)
psych::omega(maia_ea, nfactors = 1)
psych::omega(maia_nd, nfactors = 1)
psych::omega(maia_n, nfactors = 1)
psych::omega(maia_nw, nfactors = 1)
psych::omega(maia_sr, nfactors = 1)
psych::omega(maia_t, nfactors = 1)
```
